### 2023-04-27 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

    In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.

@@

    With all the data collected, classified and saved in real time, we can do further analysis and studies. For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X FlowRate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researchs, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.

@@

    The control sequence is the only from our list of sequences that actually uses the feedback value. 
    As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.

@@

>>>>

    In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.

@@

    With all the data collected, classified and saved in real time, we can do further analysis and studies. For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researches, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.

@@

    The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
    As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.
    A simple controller algorithm is represented in \ref{alg:simple_controller}, and it was used as a proof of concept.

@@

    \section{Chapter conclusion}
